Preliminary insights into the use of pottery and culinary practices at Guijiabao site in southwest China

### 2024-04-29 analysis/paper/paper.Rmd
minor edit

# Conclusion
This paper presents a preliminary result investigating pottery use and culinary practices at Guijiabao in the Yanyuan area, middle Hengduan mountain range, through organic residue analyses. Despite the small sample size, our results reveal a relatively diverse range of food categories cooked in pottery during the Neolithic period, including ruminant adipose fats, plants such as broomcorn millet, and non-ruminant sources. In the historical period, mixtures of ruminant adipose fats and non-ruminant fats were identified. Non-ruminant fats could have originated from C~3~ plants, pigs, or freshwater resources.

>>>>

# Conclusion
This paper presents preliminary results investigating pottery use and culinary practices at Guijiabao in the Yanyuan area, middle Hengduan mountain range, through organic residue analyses. Despite the small sample size, our results reveal a relatively diverse range of food categories cooked in pottery during the Neolithic period, including ruminant adipose fats, plants such as broomcorn millet, and non-ruminant sources. In the historical period, mixtures of ruminant adipose fats and non-ruminant fats were identified. Non-ruminant fats could have originated from C~3~ plants, pigs, or freshwater resources.
